---
title: "Challenge-4"
author: "Daniel Tan"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
p.comment {
background-color: #DBDBDB;
padding: 10px;
border: 1px solid black;
margin-left: 25px;
border-radius: 5px;
font-style: italic;
}

</style>

## Questions
<br>

Load the "CommQuest2023.csv" dataset using the `read_csv()` command and assign it to a variable named "comm_data." 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(tidyverse)
read_csv("CommQuest2023_Larger.csv")
comm_data<-read_csv("CommQuest2023_Larger.csv")
```
<br>


#### Question-1: Communication Chronicles

Using the select command, create a new dataframe containing only the "date," "channel," and "message" columns from the "comm_data" dataset.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data%>%
  select(date,channel,message)
```
<br>

#### Question-2: Channel Selection

Use the filter command to create a new dataframe that includes messages sent through the "Twitter" channel on August 2nd.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data%>%
  filter(
    channel == "Twitter",
    date == "2023-08-02"
  ) %>%
  select(date,channel,message)
```
<br>

#### Question-3: Chronological Order

Utilizing the arrange command, arrange the "comm_data" dataframe in ascending order based on the "date" column.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data%>%
  arrange(date)
```
<br>

#### Question-4: Distinct Discovery

Apply the distinct command to find the unique senders in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
unique_senders <- distinct(comm_data, sender)
```
<br>

#### Question-5: Sender Stats

Employ the count and group_by commands to generate a summary table that shows the count of messages sent by each sender in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data%>%
  group_by(sender) %>%
  summarise(count=n())
```
<br>

#### Question-6: Channel Chatter Insights

Using the group_by and count commands, create a summary table that displays the count of messages sent through each communication channel in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data%>%
  group_by(channel) %>%
  summarise(count=n())
```
<br>

#### Question-7: Positive Pioneers

Utilize the filter, select, and arrange commands to identify the top three senders with the highest average positive sentiment scores. Display their usernames and corresponding sentiment averages.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data%>%
  group_by(sender) %>%
  summarise(mean_sentiment=mean(sentiment))%>%
  filter(mean_sentiment>0)%>%
  arrange(desc(mean_sentiment))

```
<br>

#### Question-8: Message Mood Over Time

With the group_by, summarise, and arrange commands, calculate the average sentiment score for each day in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data%>%
  group_by(date)%>%
  summarise(mean_sentiment=mean(sentiment))
```
<br>

#### Question-9: Selective Sentiments

Use the filter and select commands to extract messages with a negative sentiment score (less than 0) and create a new dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data%>%
  filter(
    sentiment < 0
  )
```
<br>

#### Question-10: Enhancing Engagement

Apply the mutate command to add a new column to the "comm_data" dataframe, representing a sentiment label: "Positive," "Neutral," or "Negative," based on the sentiment score.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data %>%
  mutate(sentiment_label = ifelse(sentiment > 0, "Positive",
                   ifelse(sentiment == 0, "Neutral", "Negative")))
```
<br>

#### Question-11: Message Impact

Create a new dataframe using the mutate and arrange commands that calculates the product of the sentiment score and the length of each message. Arrange the results in descending order.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data%>%
  mutate(sentiment_product = sentiment * nchar(message)) %>%
  arrange(desc(sentiment_product))
```
<br>

#### Question-12: Daily Message Challenge

Use the group_by, summarise, and arrange commands to find the day with the highest total number of characters sent across all messages in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
comm_data%>%
  group_by(date)%>%
  summarise(total_char=sum(nchar(message)))%>%
  arrange(desc(total_char))
  
```
<br>

#### Question-13: Untidy data

Can you list at least two reasons why the dataset illustrated in slide 10 is non-tidy? How can it be made Tidy?

**Solution:** _The dataset contains hierarchical data structures, where data is organized in a way that doesn't easily fit the tidy data principles of one variable per column and one observation per row. The variables are also in rows instead of columns. You may need to perform data preprocessing steps, such as data cleaning, reshaping, and restructuring, to transform it into a format that conforms to the principles of tidy data. Each variable forms a column. Each observation forms a row. Each type of observational unit forms a table. You might need to use tools like R or Python with packages such as tidyr or pandas to restructure the dataset to fit these principles._