---
title: "Challenge-7"
author: "Daniel Tan"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Solutions:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library(tidyverse)
library(palmerpenguins)
glimpse(penguins)

```
<br>

#### Making a plot with ggplot

```{r, eval=TRUE,echo=TRUE}
# Enter code here
ggplot(data = penguins,
       mapping = aes(x = bill_depth_mm,
                     y = bill_length_mm,
                     colour = species,
                     shape = island,
                     size = body_mass_g,
                     alpha = flipper_length_mm)) +
  geom_point() +
  labs(title = "Bill depth and length",
       subtitle = "Dimensions for Adelie, Chinstrap and Gentoo Penguins",
       x = "Bill Depth(mm)",
       y = "Bill Length (mm)",
       colour = "Species",
       caption = "Source: Palmer Station LTER") +
  scale_colour_viridis_d()


```
<br>

#### Facets

```{r, eval=TRUE,echo=TRUE}
ggplot(penguins, aes(x = bill_depth_mm, y = bill_length_mm)) + geom_point() +
  facet_grid(species ~ sex)


```

#### Take a peek at data

```{r, eval=TRUE,echo=TRUE}
library(openintro)
glimpse(loans_full_schema)


```

#### Selected variables

```{r, eval=TRUE,echo=TRUE}
loans <- loans_full_schema %>%
  select(loan_amount, interest_rate, term, grade, state, annual_income, homeownership, debt_to_income)
glimpse(loans)


```

#### Histogram

```{r, eval=TRUE,echo=TRUE}
ggplot(loans) + aes(x = loan_amount) +
  geom_histogram()


```

#### Histograms and binwidth=1000

```{r, eval=TRUE,echo=TRUE}
# binwidth = 1000
ggplot(loans, aes(x = loan_amount)) +
  geom_histogram(binwidth = 1000)

```

#### Histograms and binwidth=5000

```{r, eval=TRUE,echo=TRUE}
# binwidth = 5000
ggplot(loans, aes(x = loan_amount)) +
  geom_histogram(binwidth = 5000)

```

#### Histograms and binwidth=20000

```{r, eval=TRUE,echo=TRUE}
# binwidth = 20000
ggplot(loans, aes(x = loan_amount)) +
  geom_histogram(binwidth = 20000)

```

#### Customising histograms

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
  geom_histogram(binwidth = 5000) +
  labs(x = "Loan amount ($)", y = "Frequency", title = "Amounts of Lending Club Loans")


```

#### Fill with a categorical variable

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
  geom_histogram(binwidth = 5000, alpha = 0.5) +
  labs(x = "Loan amount ($)", y = "Frequency", title = "Amounts of Lending Club Loans")

```

#### Facet with a categorical variable

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
  geom_histogram(binwidth = 5000) +
  labs(x = "Loan amount ($)", y = "Frequency", title = "Amounts of Lending Club Loans") +
  facet_wrap(~ homeownership, nrow = 3)

```

#### Density plot

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
  geom_density()

```

#### Density plots and adjusting bandwidth

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
  geom_density(adjust = 0.5)

```

#### Customizing density plots

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount)) +
  geom_density(adjust = 2) +
  labs(x = "Loan amount ($)", y = "Density", title = "Amounts of Lending Club loans")

```

#### Adding a categorical variable

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = loan_amount, fill = homeownership)) +
  geom_density(adjust = 2, alpha = 0.5) +
  labs(x = "Loan amount ($)", y = "Density", title = "Amounts of Lending Club loans")

```

#### Box Plot

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = interest_rate)) +
  geom_boxplot()

```

#### Box plot and outliers

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = annual_income)) +
  geom_boxplot()

```

#### Adding a categoric varaiable

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = interest_rate,
                  y = grade)) +
  geom_boxplot() +
  labs(x = "Interest rate (%)", y = "Grade", title = "Interest rates of Lending Club loans")

```

#### Scatterplot

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
  geom_point()

```

#### Hex plot

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = debt_to_income, y = interest_rate)) +
  geom_hex()

```

#### Hex plot

```{r, eval=TRUE,echo=TRUE}
ggplot(loans %>% filter(debt_to_income < 100),
       aes(x = debt_to_income, y = interest_rate)) +
  geom_hex()

```

#### Bar plot

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = homeownership)) +
  geom_bar()

```

#### Segmented Bar Plot

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = homeownership,
                  fill = grade)) +
  geom_bar()

```

#### Segmented Bar Plot

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = homeownership,
                  fill = grade)) +
  geom_bar(position = "fill")

```

#### Customizing bar plots

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(y = homeownership, fill = grade)) + geom_bar(position = "fill") +
  labs(x = "Proportion", y = "Homeownership", fill = "Grade", title = "Grades of Lending CLub loans")

```

#### Violin plots

```{r, eval=TRUE,echo=TRUE}
ggplot(loans, aes(x = homeownership, y = loan_amount)) +
  geom_violin()
```

#### Ridge plots

```{r, eval=TRUE,echo=TRUE}
library(ggridges)
ggplot(loans, aes(x = loan_amount, y = grade, fill = grade, color = grade)) +
  geom_density_ridges(alpha = 0.5)
```

#### 

```{r, eval=TRUE,echo=TRUE}

```

#### 

```{r, eval=TRUE,echo=TRUE}

```

#### 

```{r, eval=TRUE,echo=TRUE}

```

#### 

```{r, eval=TRUE,echo=TRUE}

```